An assessment of photometric redshift PDF performance in the context of LSST

### 2018-11-20 paper/main.tex
add skynet bonnett ref

In addition to packages cited in the text, analyses performed in this paper used the following software packages: \textsc{Numpy} and \textsc{Scipy} \citep{numpyscipy}, \textsc{Matplotlib} \citep{matplotlib}, \textsc{Seaborn} \citep{seaborn},

>>>>

In addition to packages cited in the text, analyses performed in this paper used the following software packages: \textsc{Numpy} and \textsc{Scipy} \citep{numpyscipy}, \textsc{Matplotlib} \citep{matplotlib}, \textsc{Seaborn} \citep{seaborn}, \textsc{minFunc} \citep{minfunc}, \textsc{pySkyNet} \citep{pyskynet}, and {\textsc photUtils} from the LSST simulations package \citep{lsstphotutils}.
